Inferring Graphics Programs from Images

### 2017-05-06 paper.tex
new introduction

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR. When we
have the generative model (the rendering function), we need not solve
an unsupervised or reinforcement learning problem.

\begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer} (canvas.east);

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
\end{tikzpicture}

@@

>>>>

\textbf{Comment for reader: this paragraph is a little grandiose and goes
  beyond what we've actually done. But these are the kinds of things
  that motivate the work, and I think that in some form these ideas
  should be in the introduction or the conclusion.} How could an agent go from noisy,
high-dimensional perceptual input to a symbolic, abstract object, like
a computer program?  Here we consider this problem within the context
of \emph{graphics program synthesis}.  We develop an approach for
converting natural images, such as hand drawings, into executable
source code for drawing the original image.
The source code captures not just the objects in the image,
but also describes their geometric relationships.

High dimensional perceptual input is ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions. Our hypothesis is that the execution trace of the
program is better aligned with the perceptual input, and that the
trace can act as a kind of bridge between perception and programs. We
test this hypothesis by developing a model that learns to map from an
image to the execution trace of the graphics program that drew it.
With the execution trace in hand, we can bring to bear techniques from
the program synthesis community to recover the latent graphics program.

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR. When we
have the generative model (the rendering function) and treat the trace
as fully observed, we need not solve an unsupervised or reinforcement
learning problem.

\begin{figure}
  \begin{tikzpicture}
  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
  % draw partial image on canvas
  \draw (0.5cm,-4cm) circle (0.1875cm);
  \draw (1.2cm,-4.3) circle (0.1875cm);
  \draw (0.85cm,-4.6) circle (0.1875cm);

@@

  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer: \LaTeX} (canvas.east);

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
  \end{figure}

\begin{table}
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|CIRCLE|$(x,y)$
    \end{tabular}& Circle at $(x,y)$\\
  \begin{tabular}{l}
    \verb|RECTANGLE|$(x_1,y_1,x_2,y_2)$
    \end{tabular}&Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$\\
  \begin{tabular}{l}
    \verb|LINE|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
    \end{tabular}&Line from $(x_1,y_1)$ to  $(x_2,y_2)$, optionally with an arrow and/or dashed\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&Finishes execution trace inference
\\  \bottomrule
\end{tabular}
\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

@@

\section{Synthesizing graphics programs from execution traces}

\begin{table}
  \begin{tabular}{rl}
  Program$\to$&Command; $\cdots$; Command\\
  Command$\to$&\texttt{CIRCLE}(Expression,Expression)\\
  Command$\to$&\texttt{RECTANGLE}(Expression,Expression,Expression,Expression)\\
  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Command$\to$&\texttt{FOR}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
  Var$\to$&A free (unused) variable\\
  \mathcal{Z}$\to$&an integer\\
  Axis$\to$&\texttt{X = }\mathcal{Z}\\
  Axis$\to$&\texttt{Y = }\mathcal{Z}
  \end{tabular}
  \caption{Grammar over graphics programs. We allow loops (\texttt{FOR}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
  \end{table}
